---
output: github_document
---

```{r setup, include = FALSE}
# The README markdown generate by this rmd file, please edit the content within this R markdown.
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  message = FALSE,
  error = FALSE,
  warning = FALSE,
  fig.path = "plot/",
  fig.align = "center",
  fig.width = 6,
  fig.height = 4
)
```

```{r library}
library(data.table)
library(tidyverse)
library(lubridate)
library(brotools)
```

```{r write_sample_train, eval=FALSE}
set.seed(001)
sample_train <- fread("../data/train_integ_2017.csv", nThread = parallel::detectCores()) %>% 
  as_tibble() %>%
  sample_frac(0.1,)
fwrite(sample_train, "../data/sample_train.csv")
```

```{r load_data}
sample_train <- fread("../data/sample_train.csv", 
                      nThread = parallel::detectCores(),
                      stringsAsFactors = TRUE) %>% 
  as_tibble() %>%
  mutate(date = ymd(date))
sample_train$store_nbr <- as.factor(sample_train$store_nbr)
sample_train$cluster <- as.factor(sample_train$cluster)
sample_train$item_nbr <- as.factor(sample_train$item_nbr)
sample_train$class <- as.factor(sample_train$class)
sample_train$perishable <- as.factor(sample_train$perishable)
```

# Grocery Sales Forecasting - Report

### Data Files

* [`README.Rmd`](https://github.com/Jiaying-Wu/Grocery-Sales-Forecasting/blob/master/report/README.Rmd): R markdown to generate this data insight of Corporación Favorita Grocery Sales data.

## Report

In order to speed up the visulization, this report only using 10% of our integrated training set, that is 2.3 millions records.

#### `unit_sales`

```{r plot_unit_sales}
sample_train %>%
  ggplot(aes(x= unit_sales)) +
  geom_histogram(binwidth = 0.3, fill = "lightblue") +
  scale_x_log10() +
  theme_blog() +
  ggtitle("Histogram of Unit Sales")
```

```{r summary_unit_sales}
summary(sample_train$unit_sales)
```

It suggested most of the item sold less than 10 units per supermarket per day.

#### `date`

```{r plot_date}
total_us_date <- sample_train %>%
  group_by(date) %>%
  summarise(total_unit_sales = sum(unit_sales)) 

total_us_date %>%
  ggplot(aes(x = date, y = total_unit_sales)) +
  geom_line(color = "white") +
  theme_blog() +
  ggtitle("Total Unit Sales via Date")
```

The plot suggested strong seasonality in the total unit sale.

#### `store_nbr`: store id.

```{r plot_store_nbr,fig.height=4, fig.width=10}
sample_train %>%
  ggplot(aes(x = store_nbr, y = unit_sales, color = store_nbr)) +
  geom_boxplot() +
  scale_y_log10() +
  theme_blog() +
  ggtitle("Boxplot of Daily Unit Sales in Each Store") +
  theme(legend.position = "none") +
  xlab("store number")
```

In general, the median unit sale of 54 store is similiar, the plot suggest `store_nbr` can explain some of variation in `unit_sales`. However, level merging of `store_nbr` might required.

#### `item_nbr`: item id.

```{r plot_item_nbr}
mean_us_item <- sample_train %>%
  group_by(item_nbr) %>%
  summarise(mean_unit_sales = mean(unit_sales))

mean_us_item %>%
  ggplot(aes(x = as.numeric(item_nbr), y = mean_unit_sales)) +
  geom_line(color = "lightblue") +
  scale_y_log10() +
  theme_blog() +
  ggtitle("Mean Unit Sales of Each Item") +
  theme(legend.position = "none") +
  xlab("item number")
```

```{r item_num}
NROW(unique(sample_train$item_nbr))
```

That is 4000 different items, the item id should be consider as factor type, plot in numerical order only in visualization purpose. The plot suggested `item_nbr` can explain a lot varaition of `unit_sales`. However, level merging of `item_nbr` might required.

#### `onpromotion`: wether on promotion.

```{r plot_onpromotion}
sample_train %>%
  ggplot(aes(x = onpromotion, y = unit_sales, color = onpromotion)) +
  geom_boxplot() +
  scale_y_log10() +
  theme_blog() +
  theme(legend.position = "none") +
  ggtitle("Boxplot of Unit Sales via Promotion")
```

The plot suggested the unit sales will slightly increased while the item is on promotion.

#### `family`: item family.

```{r plot_family,fig.height=4, fig.width=10}
sample_train %>%
  ggplot(aes(x = family, y = unit_sales, color = family)) +
  geom_boxplot() +
  scale_y_log10() +
  scale_x_discrete(label = abbreviate) +
  theme_blog() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Boxplot of Unit Sales via Item Family") +
  xlab("item family")
```

```{r num_family}
NROW(unique(sample_train$family))
```

33 level in `family`, this variable explain lot of variation of `unit_sales`. Consider it is a fatcor variable, level might a bit too much. Since `family` is a feature related to item, we can integrated `family` and `item_nbr` to generate new features via clustering.

#### `class`: item class.

```{r plot_class}
mean_us_class <- sample_train %>%
  group_by(class) %>%
  summarise(mean_unit_sales = mean(unit_sales))

mean_us_class %>%
  ggplot(aes(x = as.numeric(class), y = mean_unit_sales)) +
  geom_line(color = "lightgreen") +
  #scale_y_log10() +
  theme_blog() +
  ggtitle("Mean Unit Sales of Item Class") +
  xlab("item class")
```

```{r num_class}
NROW(unique(sample_train$class))
```

That is 331 different item class. The item class should be consider as factor type, plot in numerical order only in visualization purpose. The plot suggested `class` can explain a lot varaition of `unit_sales`. 

Since `class` is also a feature related to item, we can integrated `class`, `family` and `item_nbr` to generate new features via item clustering.

#### `perishable`: wether item is perishable.

```{r plot_perishable}
sample_train %>%
  ggplot(aes(x = perishable, y = unit_sales, color = perishable)) +
  geom_boxplot() +
  scale_y_log10() +
  theme_blog() +
  theme(legend.position = "none") +
  ggtitle("Boxplot of Unit Sales via Perishable Item")
```

In this plot, 1 mean the item is perishable and 0 is the contrast. The plot suggested the perishable item will have a higher sale in units.

#### `city`

```{r plot_city, fig.height=4, fig.width=8}
sample_train %>%
  ggplot(aes(x = city, y = unit_sales, color = city)) +
  geom_boxplot() +
  scale_y_log10() +
  scale_x_discrete(label = abbreviate) +
  theme_blog() +
  theme(legend.position = "none") +
  ggtitle("Boxplot of Unit Sales via City")
```

The supermarket in city Quito have the highest mean unit sales comparing others.

```{r num_city}
NROW(unique(sample_train$city))
```

#### `state`

```{r plot_state, fig.height=4, fig.width=8}
sample_train %>%
  ggplot(aes(x = state, y = unit_sales, color = state)) +
  geom_boxplot() +
  scale_y_log10() +
  scale_x_discrete(label = abbreviate) +
  theme_blog() +
  theme(legend.position = "none") +
  ggtitle("Boxplot of Unit Sales via State")
```

```{r num_state}
NROW(unique(sample_train$state))
```

That is 22 city in 16 state of this dataset, both of them explain some of the variation in `unit_sales`. However, some of the level share the similar mean in both varaible. Since the number of city only slightly smaller than the number of state, we can integrated `city` and ` state` to generate new features.

#### `type`: store type.

```{r plot_type}
sample_train %>%
  ggplot(aes(x = type, y = unit_sales, color = type)) +
  geom_boxplot() +
  scale_y_log10() +
  theme_blog() +
  theme(legend.position = "none") +
  ggtitle("Boxplot of Unit Sales via Store Type") +
  xlab("store type")
```

The item in store type A have the higest mean unit sales and item in store type E have the lowest mean unit sales. The mean unit sale in each store type share the similar value, future level merging for `type` might required.

#### `cluster`: store cluster.

```{r plot_cluster, fig.height=4, fig.width=8}
sample_train %>%
  ggplot(aes(x = cluster, y = unit_sales, color = cluster)) +
  geom_boxplot() +
  scale_y_log10() +
  theme_blog() +
  theme(legend.position = "none") +
  ggtitle("Boxplot of Unit Sales via Store Cluster") +
  xlab("store cluster")
```

The plot suggested supermarket in cluster 5, 8, 11 and 14 have a higher mean unit sales than others. Since some of the cluster have the similar mean unit sale, future level merging for `type` might required.

#### `dcoilwtico`: oil price.

```{r plot_dcoilwtico}
mean_us_dcoilwtico <- sample_train %>%
  group_by(dcoilwtico) %>%
  summarise(mean_unit_sales = mean(unit_sales))

mean_us_dcoilwtico %>%
  ggplot(aes(x = dcoilwtico, y = mean_unit_sales)) +
  geom_point(color = "purple") +
  theme_blog() +
  geom_smooth(se = FALSE) +
  ggtitle("Mean Unit Sales via Oil price") +
  xlab("oil price")
```

The plot suggested the mean unit sales is positive associated with the oil price.

