---
output: github_document
---

```{r setup, include = FALSE}
# The README markdown generate by this rmd file, please edit the content within this R markdown.
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  message = FALSE,
  error = FALSE,
  warning = FALSE,
  fig.path = "plot/",
  fig.align = "center"
)
```

```{r library}
library(data.table)
library(tidyverse)
library(lubridate)
library(brotools)
```

```{r load_data}
set.seed(001)
sample_train <- fread("../data/train_integ_2017.csv", nThread = parallel::detectCores()) %>% 
  as_tibble() %>%
  sample_frac(0.1)
```

# Grocery Sales Forecasting - Report

The completed data set contain 125+ millions grocery sale records, because the goal is to forecast the future value. Using data far behind the forecasting date might cause the result unreliable. In this case, we only using the sale records after `2017-01-01` for training purpose. After integrated `train` with `items`, `stores` and `oil`, we got 23+ millions records along with 12 features.

In order to speed up the visulization, this report only using 10% of our integrated train set, that is 2.3 millions records.

#### `unit_sales`

```{r plot_unit_sales}
sample_train %>%
  ggplot(aes(x= unit_sales)) +
  geom_histogram(binwidth = 0.3, fill = "lightblue") +
  scale_x_log10() +
  theme_blog() +
  ggtitle("Histogram of Unit Sales")
```

```{r summary_unit_sales}
summary(sample_train$unit_sales)
```

It suggested most of the sales less than 10 units per day in each supermarket.

#### `date`

```{r}
sample_train %>%
  
```

